Non-Vertical Cultural Transmission and the\\ Evolution of Cooperation

### 2020-08-19 ms/main.tex
vertical threshold

We redefine the cost boundaries,
the \emph{cost boundaries},
\begin{equation} \label{eq:cost_boundaries_v}
\begin{aligned}
\hat\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{1-T_B}, \quad
\hat\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)}.
\end{aligned}
\end{equation}
The following result summarizes the possible outcomes.
\\

\begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_3$ (\autoref{eq:cost_boundaries_v}):

@@

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(iiia)} $T_A<T_B$ and $v>\frac{T_B-T_A}{1-T_A}$ and $c < \hat\gamma_2$; or
	if \emph{(iiib)} $T_A<T_B$ and $v<\frac{T_B-T_A}{1-T_A}$ and $c > \hat\gamma_2$.
\item \emph{Fixation of the defection}: 
	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
	if \emph{(v)} $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
\item \emph{Fixation of either phenotype depending on initial frequency}:
	if \emph{(viii)}  $T_A>T_B$ and $\beta_3<\beta_1$.
\end{enumerate}
\end{result}

>>>>

We redefine the cost boundaries,
the \emph{cost boundaries},
\begin{equation} \label{eq:cost_boundaries_v}
\begin{aligned}
\hat\gamma_1 = \frac{b v \alpha T_A + (T_A - T_B)}{1-T_B}, \quad
\hat\gamma_2 = \frac{b v \alpha T_B + (1+b) (T_A - T_B)}{v(1-T_B) + (1-v)(T_A-T_B)},
\end{aligned}
\end{equation}
and define a vertical transmission threshold,
\begin{equation} \label{eq:v_threshold}
\hat v = \frac{T_B - T_A)}{1-T_A} \,.
\end{equation}

The following result summarizes the possible outcomes.
\\

\begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
With vertical, horizontal, and oblique transmission, the cultural evolution of a cooperator phenotype will follow one of the following scenarios depending on the cost boundaries $\hat\gamma_1$ and $\hat\gamma_3$ (\autoref{eq:cost_boundaries_v}) and the vertical threshold $\hat v$ (\autoref{eq:v_threshold}) :

@@

% in gamma
\begin{enumerate}
\item \emph{Fixation of cooperation}: 
	if \emph{(i)} $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
	if \emph{(ii)} $T_A>T_B$ and $c < \hat\gamma_1$; or 
	if \emph{(iiia)} $T_A<T_B$ and $v>\hat v$ and $c < \hat\gamma_2$; or
	if \emph{(iiib)} $T_A<T_B$ and $v<\hat v$ and $c > \hat\gamma_2$.
\item \emph{Fixation of the defection}: 
	if \emph{(iv)}  $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
	if \emph{(v)} $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
	if \emph{(vi)} $T_A<T_B$ and $\beta_3<0$.
\item \emph{Coexistence of both phenotypes at $\hat{p}^*$}: 
	if \emph{(vii)} $T_A < T_B$ and $0<\beta_3<\beta_1$.
\item \emph{Fixation of either phenotype depending on initial frequency}:
	if \emph{(viii)}  $T_A>T_B$ and $\beta_3<\beta_1$.
\end{enumerate}
\end{result}
